%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Publications}

\cvsubsection{Academic Journals}

\begin{cvparagraph}
%---------------------------------------------------------
\textbf{Sun, George L.}, and Angela M. Belcher. ``Engineering supramolecular forming proteins to chelate heavy metals for waste water remediation.'' (2020). \textit{in submission}.

\textbf{Sun, George L.}, Erin E. Reynolds, and Angela M. Belcher. ``Using yeast to sustainably remediate and extract heavy metals from wastewaters.'' \textit{Nature sustainability} (2020). \textit{in review}.

Gilbert, C., Tang, T. C., Ott, W., Dorr, B. A., Shaw, W. M., \textbf{Sun, G. L.}, ... \& Ellis, T. ``Living materials with programmable functionalities grown from engineered microbial co-cultures.'' \textit{bioRxiv}. (2019).

\textbf{Sun, George L.}, Erin E. Reynolds, and Angela M. Belcher. ``Designing yeast as plant-like hyperaccumulators for heavy metals.'' \textit{Nature communications} 10.1 (2019): 1-12.

Shapiro, M. G., Ramirez, R. M., Sperling, L. J., \textbf{Sun, G.}, Sun, J., Pines, A., ... \& Bajaj, V. S. (2014). ``Genetically encoded reporters for hyperpolarized xenon magnetic resonance imaging.'' \textit{Nature chemistry} 6.7 (2014): 629.

\end{cvparagraph}
%---------------------------------------------------------

\cvsubsection{Web Publications}

\begin{cvparagraph}
%---------------------------------------------------------
\textbf{Sun, George L.}. ``File Structure''. \textit{Mechanical Engineering Communication Lab, MIT}. (2019). \url{https://mitcommlab.mit.edu/meche/commkit/file-structure/}.
% 6 Nov. 2019.

% Kyle McLean, Josh Peters, Divya Ramamoorthy, George Sun, Tyler Toth, Alexander Triassi, Prerna Bhargava,
McLean, K., Peters J., Ramamoorthy, D., \textbf{Sun, G.}, Toth T., Triassi A., Prerna B. ``Awesome BECL Resources''. \textit{Biological Engineering Communication Lab, MIT}. (2019). \url{https://github.com/MIT-BECL/awesome-becl-resources}.

\textbf{Sun, G.}, Wang, D., Gerarld, K. ``Air Guitar''. \textit{Instructables}. (2016). \url{
https://www.instructables.com/id/Air-Guitar/}.

\end{cvparagraph}
