%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Research Experience}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
\cventry
    {PhD, Graduate Researcher -- Belcher Lab} % Job title
    {Biomolecular Materials Group, MIT} % Organization
    {Cambridge, MA} % Location
    {Sept. 2014 - June. 2019} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Engineered yeast as a bioremediation agent to consume and recycle heavy metals, particularly from electronics and mining runoff.}
        \item {Authored and co-authored several research articles in Nature, with several utility patents emerging from this unique invention.}
        \item {Utilized laboratory techniques ranging from material science (ICP, EDX, XRD), molecular biology (PCR, genetic circuits, transformations), chemistry (chromatography, electrochemistry), and analytical tools (matplotlib, scikit-learn, tidyverse).}
        \item {Awarded several grants (NSF, Bose, CEHS) and honors for scientific talks and presentations on environmental remediation technologies.}
      \end{cvitems}
    }

%---------------------------------------------------------
 \cventry
    {Research Assistant -- Shapiro Lab} % Job title
    {Molecular Engineering Imaging and Control Group, Berkeley \& Caltech} % Organization
    {Berkeley \& Pasadena, CA} % Location
    {Jan. 2011 - Aug. 2014} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Conducted research in biomolecular tools such as stem cell therapy and biological contrast agents for medical imaging.}
        \item {Independently researched the effects of metallo-enzymes on enhancing the magnetic properties of neurological systems for NMR and MRI.}
        \item {Transitioned to Caltech's Chemical Engineering department in the last year of college to finalize research.}
      \end{cvitems}
    }

%---------------------------------------------------------
 \cventry
    {Amgen Research Scholar -- Sia Lab} % Job title
    {Microfluidics for Point-of-Care Diagnostics Group, Columbia} % Organization
    {New York, NY} % Location
    {June 2013 - September 2013} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Created new experimental protocols to create PDMS scaffolds for organoid growth.}
        \item {Focused on recreating synthetic extracellular matrixes and vasculature for brown fat and hair follicle growth.}
      \end{cvitems}
    }

\end{cventries}
