%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Work Experience}

% variables
\newcommand{\patents}{3}
\newcommand{\raised}{1M}

%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
\cventry
    {CEO} % Job title
    {Nextiles, Inc.} % Organization
    {Brooklyn, NY} % Location
    {Jan. 2020 - Present} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Secured >\$\raised{} on non-dilutive grants, pre-seed round, and established a hardware manufacturing space in Brookyln, NYC.}
        \item {Collaborated with several industries in the textile, sports apparel, and medical technologies sectors.}
        \item {Led the business strategy and oversaw financials to guide the company into a sustainable and profitable trajectory.}
      \end{cvitems}
    }

\cventry
    {Co-Founder \& CTO} % Job title
    {} % Organization
    {} % Location
    {June 2019 - Dec 2019} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Tasked with developing new wearable technologies based on fabric-based sensors. Sensors are built to measure force directly from compression/bending of threads.}
        \item {Patented \patents{} unique inventions on the design, manufacturability, and application of fabric-based sensors, all approved by the USPTO.}
        \item {Completed programs such as MIT Delta V accelerator, Hubweek Demo Day, NSF I-Corps, and several other pitch and showcase events.}
      \end{cvitems}
    }

\cventry
    {Founder} % Job title
    {} % Organization
    {} % Location
    {April 2018 - May 2019}
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Founded \href{www.Nextiles.tech}{Nextiles}, a startup built on re-thinking wearable technologies through advanced sewing technologies.}
        \item {Inspired from past work in electrical engineering and material science, and motivated to merge the two together in unique ways in fabric.}
      \end{cvitems}
    }

%---------------------------------------------------------
 \cventry
    {Lead Embedded Engineer} % Job title
    {Puma \textit{X} Design Lab} % Organization
    {Cambridge \& Nuremberg} % Location
    {Jan. 2017 - Jan. 2018} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Led a team of engineers and designers with Puma's Innovation Team to redesign and instrument their line of athletic shoes}
        \item {Focused on embedding force-sensitive materials into the shoe to track gait and power using machine models.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Communication Fellow \& Instructor} % Job title
    {Communication Lab, MIT} % Organization
    {Cambridge, MA} % Location
    {Jun. 2015 - May. 2019} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Facilitated workshops and seminars on effective communication and scientific presentation.}
        \item {Worked with MIT's \textit{GEL} program and helped teach \href{Leading Creative Teams}{\textit{Leading Creative Teams}} while developing course content for MIT.}
      \end{cvitems}
    }
%---------------------------------------------------------
\end{cventries}
